\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-11 tex/paper.tex
Changed access rights definition

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Metadata for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

@@

\item[Access Matrix] \hfill \\
    The access matrix contains what containers that all the users in the system have access to. If
    A[u,c] exists in the access matrix, user \textit{u} has access to container \textit{c}.

@@

\subsection{Access rights}
Access is only handled on containers and if a user has access to a container it also has access to
all of that containers children.
The \textit{A[u,c]} notation is symbolising an access token, and if \textit{A[u,c]} exists in
the access matrix \textit{A}, user \textit{u} has full access to the container object \textit{c} and
its children.

\begin{equation}
    \begin{split}
        A[u,c] \in A \Rightarrow & u \text{ can read } c \\
        A[u,c] \in A \land \text{ read-only } \notin c \Rightarrow & u \text{ can write to } c \\
        A[u,c] \in A \land \text{ read-only } \notin c \Rightarrow & u \text{ can delete } c \\
        A[u,c] \in A \land f \in c \centernot\Rightarrow & u \text{ can delete } f 
    \end{split}
\end{equation}

@@

\vspace{2em}
\textbf{File Update}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {f \in F \\ [fileId = f.id, parent = c \dots] \in M \\ A[u,c] \in A} 
    {F \cup \{f\} \xrightarrow{u, update(fileId, f'.id)} F \cup \{f, f'\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {m \in M \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, update(m, m')} M \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:containerupdate}
%    \begin{split}
%        c' & = u, read(c) \land \\
%        c'' & = u, change(c') \land \\
%        c''' & = u, modify(c'', c) \Implies \\
%        c''' & \in C \land c \not \in C
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Container Update}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {C \cup \{c\} \xrightarrow{u, update(c, c')} C \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'.id}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {M, C \xrightarrow{[C', M'] := u, snapshot(c)} M \cup M',  C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

>>>>

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Metadata for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; access rights \\ \hline
    \end{tabular}
\end{center}

@@

\item[Access Matrix] \hfill \\
    The access matrix contains what containers that all the users in the system have access to. If
    A[u,c] is true in the access matrix, user \textit{u} has access to container \textit{c}.

@@

\subsection{Access rights}
Access is only handled on containers and if a user has access to a container it also has access to
all of that containers children.
The \textit{A[u,c]} notation is symbolising an access token. If \textit{A[u,c]} is true in the 
access matrix \textit{A}, user \textit{u} has full access to the container object \textit{c} and its
children. If it is false or if the entry does not exist in the access matrix, the user \textit{u}
does not have any access rights for \textit{c}.

\begin{equation}
    \begin{split}
        A[u,c] \Rightarrow & u \text{ can read } c \\
        A[u,c] \land \text{ read-only } \notin c \Rightarrow & u \text{ can write to } c \\
        A[u,c] \land \text{ read-only } \notin c \Rightarrow & u \text{ can delete } c \\
        A[u,c] \land f \in c \centernot\Rightarrow & u \text{ can delete } f 
    \end{split}
\end{equation}

@@

\vspace{2em}
\textbf{File Update}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {f \in F \\ [fileId = f.id, parent = c \dots] \in M \\ A[u,c]} 
    {F \cup \{f\} \xrightarrow{u, update(fileId, f'.id)} F \cup \{f, f'\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {m \in M \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \xrightarrow{u, update(m, m')} M \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:containerupdate}
%    \begin{split}
%        c' & = u, read(c) \land \\
%        c'' & = u, change(c') \land \\
%        c''' & = u, modify(c'', c) \Implies \\
%        c''' & \in C \land c \not \in C
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Container Update}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {c \in C \\ A[u,c]}
    {C \cup \{c\} \xrightarrow{u, update(c, c')} C \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'.id}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c]}
    {M, C \xrightarrow{[C', M'] := u, snapshot(c)} M \cup M',  C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.
